On the formation of H$\alpha$ line emission around classical T Tauri stars

### 2006-01-16 TTau_Halpha/kurosawa.tex
Minor chnages. Replaced the phrase "inner most" to "innermost".  (RK)
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@619 25464f21-6099-402c-b30a-640f1d40d38b

To understand how the different part of the CTTS circumstellar environment
contributes to the formation of H$\alpha$, the model space is divided
into four different regions: (1)~a central continuum source, (2)~the magnetospherical
accretion flow, (3)~the wind outflow, and (4)~the accretion
disc. Fig.~\ref{fig:config_dipolar} 
depicts the relative location of the regions in the model space. In
all regions, the density is symmetric around the z-axis. The innermost radius of
the magnetosphere at the equatorial plane coincides with the the inner
radius of the accretion disc. From the inner most part of the accretion
disc, the gas falls freely, moving along the magnetic field onto the
surface of the star. For simplicity,
the out-flowing wind component is defined only in the outside of the
largest radius of the magnetosphere (to avoid overlapping of the wind
with the magnetosphere). In the following subsections, the details
of model components will be described.
\begin{figure*}

@@

\caption{The basic model configuration. The system consists of four
components: (1)~the continuum source located at the origin $\left( o
\right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
y-axis are into the paper, (2)~the magnetospherical accretion flow,
(3)~the bipolar wind outflow, and (4)~the accretion disc. The density
distribution is symmetric around the z-axis. The innermost radius of
the magnetosphere (at the equatorial plane) coincides with the the
inner radius of the accretion disc. From the inner most part of the
accretion disc, the gas falls freely, moving along the magnetic field
onto the surface of the star. The bipolar wind starts from just
outside of the largest radius 
($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }

@@

The local mass-loss rate per unit area ($\dot{m}$) is assumed to
be proportional to the mid-plane temperature of the disc, and is a
function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
, i.e. \begin{equation}
\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
 Further, the mid-plane temperature of the disc is assumed to be expressed
as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
relation above, one finds \begin{equation}
\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
where $p=\alpha\times q$. The index of the mid-plane temperature
power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
who found the inner most part of the accretion disc has $q=-1.15$.
To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
of proportionality in equation~\ref{eq:discwind-massloss-w} is found
by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.

>>>>

To understand how the different part of the CTTS circumstellar environment
contributes to the formation of H$\alpha$, the model space is divided
into four different regions: (1)~a central continuum source, (2)~the magnetospherical
accretion flow, (3)~the wind outflow, and (4)~the accretion
disc. Fig.~\ref{fig:config_dipolar} 
depicts the relative location of the regions in the model space. In
all regions, the density is symmetric around the z-axis. The innermost radius of
the magnetosphere at the equatorial plane coincides with the the inner
radius of the accretion disc. From the innermost part of the accretion
disc, the gas falls freely, moving along the magnetic field onto the
surface of the star. For simplicity,
the out-flowing wind component is defined only in the outside of the
largest radius of the magnetosphere (to avoid overlapping of the wind
with the magnetosphere). In the following subsections, the details
of model components will be described.
\begin{figure*}

@@

\caption{The basic model configuration. The system consists of four
components: (1)~the continuum source located at the origin $\left( o
\right)$ of the cartesian coordinates $\left(x,y,z\right)$ -- the
y-axis are into the paper, (2)~the magnetospherical accretion flow,
(3)~the bipolar wind outflow, and (4)~the accretion disc. The density
distribution is symmetric around the z-axis. The innermost radius of
the magnetosphere (at the equatorial plane) coincides with the the
inner radius of the accretion disc. From the innermost part of the
accretion disc, the gas falls freely, moving along the magnetic field
onto the surface of the star. The bipolar wind starts from just
outside of the largest radius 
($R_{\mathrm{mo}}$) of the magnetosphere (dotted line). }

@@

The local mass-loss rate per unit area ($\dot{m}$) is assumed to
be proportional to the mid-plane temperature of the disc, and is a
function of the cylindrical radius $w=\left(x^{2}+y^{2}\right)^{1/2}$
, i.e. \begin{equation}
\dot{m}\left(w\right)\propto T\left(w\right)^{\alpha}\,\,.\label{eq:discwind-massloss-temp}\end{equation}
 Further, the mid-plane temperature of the disc is assumed to be expressed
as a power-law in $w$; thus, $T\propto w^{q}$. Using this in the
relation above, one finds \begin{equation}
\dot{m}\left(w\right)\propto w^{p}\label{eq:discwind-massloss-w}\end{equation}
where $p=\alpha\times q$. The index of the mid-plane temperature
power law is adopted from the dust radiative transfer model of \citet{whitney:2003a}
who found the innermost part of the accretion disc has $q=-1.15$.
To be consistent with the collimated disc-wind model of \citet{krasnopolsky:2003}
who used $p=-3/2$, the value of $\alpha$ is set to 1.3. The constant
of proportionality in equation~\ref{eq:discwind-massloss-w} is found
by integrating $\dot{m}$ from $R_{\mathrm{wi}}$ to $R_{\mathrm{wo}}$,
and the normalising the value to the total mass-loss rate $\dot{M}_{\mathrm{dw}}$.
